\cventry{2016}
    {Business application for Indian mid sized construction companies}
    {}
    {}
    {}
    {Web based business application developed to manage salaries of employees working at different construction sites. Expenditure reports can be generated site wise, month wise and year wise. There is also a feature to keep and view historical records of employees' per day rates. Project is powered by NodeJS at back-end and Google's AngularJS front-end framework at front-end. Angular Material and MaterialiseCSS (Google's material design specifications based CSS framework) is used for UI/UX.
        \hfill
        \href{https://bitbucket.org/harman052/gh}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}


\cventry{2015}
    {WordPress theme development}
    {}
    {}
    {}
    {An easily customizable flat design theme for creating stunning and responsive WordPress websites. Equipped with inbuilt options to create ravishing and striking portfolio, it is suitable for people ranging from individuals to small and medium enterprises. It is backed by HTML5, CSS3, AJAX, JQuery and PHP.
        \hfill
        \href{https://bitbucket.org/harman052/csiom_theme}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}


\cventry{2013}
    {Google Summer of Code-2013 (GSoC): Online Geometry Viewer (OGV)}
    {}
    {}
    {}
    {A program organized and funded by Google to promote open source software development, I was selected by BRL-CAD, an open source CAD software community. My project was to develop Online Geometry Viewer (OGV), a web application for viewing BRL-CAD's native format (.g format) on web browsers. three.js, a webGL based JavaScript library was used at back-end for 3D geometry visualization.
        \hfill
        \href{https://github.com/BRL-CAD/geometry_viewer}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}


\cventry{2012}
    {Web based CAD model generator}
    {}
    {}
    {}
    {As part of six months industrial training, I developed a web application in C++ that helps to create customized model of water tank with minimum efforts, without any need of having expertise knowledge of CAD systems. User just need to fill the form with water tank parameters and back-end system automatically generates the corresponding model. \textbf{Project is written in C++ and file parsing is done with shell scripting. CGI is used as an interface between C++ executables and web browser}.
            \hfill
        \href{https://github.com/GreatDevelopers/wBRLCAD/tree/master/civil/watertank}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}
